
As in Project 1, code submission for checkpoint and the final deadline will be done 
through \jc{Autolab (autolab.cs.cmu.edu).}
Every checkpoint will be a git tag in the code repo. To create a tag, run
\[
\texttt{git tag -a checkpoint-\textit{<num>} -m \textit{<message>} [\textit{<commit hash>}]}
\]
with appropriate checkpoint number and custom message filled in. (Put whatever
you like for the message --- git won't let you omit it.) The optional commit
hash can be used to specify a particular commit for the tag; it you omit it,
the current commit is used. 
\noindent For the checkpoint, you will be expected to have a working Makefile, and 
whatever source needed to compile a working binary.  \textbf{Checkpoints that do not compile will
NOT be graded.}  
\jc{To submit your code, make a tarball file of your repo after you tag it. Then login to autolab website,
choose \texttt{15-441: Computer Networks (S19) -> project2cp<{\it N}>}, and then upload your tarball.}
The submitted tarball should contain a directory named \texttt{15-441-project-2}, which has 
the following files that implement all required functionality:
\begin{itemize}
\item Makefile:  Make sure all the variables and paths are set correctly such 
that your program compiles in the hand-in directory. Running \texttt{make test} should run your testing code.
%Makefile should build the executable ``peer'' that runs on the andrew machines.
\item All of your source code files and test files. (files ending in .c, .h, etc. only, no .o files and no executables)
\item readme.txt: File containing a thorough description of your design and implementation. If you use any additional packet headers, please document them 
here. 
\item tests.txt: File containing documentation of your test cases and any known issues you have.

\item submit.pcap: Your PCAP submission file from running the functionality code in server.c and client.c from the starter code (for a larger file transfer). 

\item graph.pdf: Your graph of the currently unacked packets in flight vs time computed from submit.pcap. 
\end{itemize}

If you have an issue with uploading large files to Autolab, follow these directions: \url{https://piazza.com/class/jqfmjnmztjt4rv?cid=792}.


